\LARGE \bf Human-Robot Interaction: A Deliberative Architecture

### 2013-07-26 paper.tex
Expand section on pyrobots. Give details on actions available

Our robot execution controllers (OpenPRS-based {\sc Shary} or Python-based {\sc
pyRobots}) have deep integration with the knowledge base. It serves as the
primary source of information for semantic-aware decision-making.

@@

The action execution and monitoring task involves the motion and task
planning, the effectors and the dedicated robot controller activity
(Figure~\ref{architecture_fg}).

\paragraph{Human aware motion, placement and manipulation planning}
In our scenarios, actions are only object manipulation actions: Pick,
Place, Throw, Give. Motion and Task planning allows to compute final
object placement, grasp and arm motion trajectories taking into
account task specific constraints and human postures, abilities and
preferences: see \cite{Sisbot2008, Mainprice2011, Pandey2010} for
details.

>>>>

Our robot execution controllers (OpenPRS-based {\sc Shary} or Python-based {\sc
pyRobots}) rely on extensive integration with the knowledge base. It serves as the
primary source of information for semantic-aware decision-making.

@@

Action execution and monitoring is the central activity of the robot executive
controller, and involves interaction with most of the components presented on
Figure~\ref{fig|archi}.

Like most robotic architecture, actions are split into \emph{atomic actions}
and more complex \emph{tasks}. Tasks are created either statically or dynamically.
The {\sc pyRobots} controller, for instance, combines the actions listed in
table~\ref{table|pyrobots_actions} to implement the high-level tasks it exposes: {\tt
lookAt}, {\tt moveTo}, {\tt getFromHuman}, {\tt showObject}, {\tt giveObject},
{\tt pickObject}, {\tt bringObject}, {\tt putObject}, {\tt hideObject}.

Our other controller, {\sc Shary}, relies on the symbolic task planner to
generate at runtime suitable tasks.

\begin{table}
\begin{center}
\begin{tabular}{p{8cm}}
\hline
    {\bf Manipulation} \\
     {\tt attachobject}, {\tt basicgive}, {\tt basictake}, {\tt close\_gripper}, {\tt configure\_grippers}, {\tt grab\_gripper}, {\tt handover}, {\tt hide}, {\tt open\_gripper}, {\tt pick}, {\tt put}, {\tt put\_accessible}, {\tt release\_gripper}, {\tt show}, {\tt take} \\
\hline
    {\bf Gaze control} \\
     {\tt glance\_to}, {\tt look\_at}, {\tt sweep}, {\tt switch\_active\_stereo\_pair}, {\tt track}, {\tt cancel\_track} \\
\hline
    {\bf Navigation} \\
     {\tt carry}, {\tt follow}, {\tt cancel\_follow}, {\tt goto}, {\tt moveclose}, {\tt waypoints} \\
\hline
    {\bf Local navigation} \\
     {\tt dock}, {\tt rotate}, {\tt translate} \\
\hline
    {\bf Posture configuration} \\
     {\tt extractpose}, {\tt idle}, {\tt manipose}, {\tt movearm}, {\tt rest}, {\tt setpose}, {\tt settorso}, {\tt tuckedpose} \\
\hline
\end{tabular}
\end{center}
\caption{Main {\sc pyRobots} \emph{actions}, sorted by categories. These
actions are combined at runtime into higher-level \emph{tasks}.}

\label{table|pyrobots_actions}
\end{table}

\paragraph{Human aware motion, placement and manipulation planning}
Manipulation and navigation actions listed in
table~\ref{table|pyrobots_actions} rely on a collection of dedicated 3D motion
planner to generate movements that are aware of surrounding humans. Robot
placement and end-effectors trajectories are computed on-line to allow object
manipulation that take into account task specific constraints and human
postures, abilities and preferences. \cite{Sisbot2008, Mainprice2011,
Pandey2010} detail these techniques.
